---
title: "The homework for the next class, Tuesday, Oct 26th"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

The homework for the next class, Tuesday, Oct 26th

I would want to ask you to pick a data set from `MASS` package and make a description of it in a simple text file (a TXT file will do) using the tools I have shown you in the class.  

Checking whether `MASS` package is installed and loading it:

```{r}
library(MASS)
```

Checking out the list of the data sets available in the `MASS` package:

```{r, eval=FALSE}
MASS::
```


Let's say, you chose `Cars93` (`MASS::Cars93`) data set to be the object of your study.

Assigning `Cars93` to a variable:

```{r}
x <- MASS::Cars93
```

Finding out the dimension of `x` (the variable contains `Cars93` data set):

```{r}
dim(x)
```

Data set `Cars93` is 93 lines long and 27 columns wide, that is, `Cars93` data frame contains 93 observations (cases, cars) described by 27 various features (parameters).


Structure of the data frame - name, type and preview of data in each column:

```{r}
str(x)
```

Checking out the names of the features (the column's names of `Cars93` data set), one by one:

```{r}
names(x)
```

Checking out the first six 6 of lines of `x` (that contains `Cars93` data set):

```{r}
head(x)
```

Take a look at each variable of `x`:

```{r}
x$Manufacturer
```

```{r}
x$Model
```

```{r}
x$Type
```

```{r}
x$Min.Price
```

```{r}
x$Price
```

```{r}
x$Max.Price
```

and so on...


Find out the type of each feature of `Cars93` data set

```{r}
class(x$Manufacturer)
```

```{r}
class(x$Model)
```
```{r}
class(x$Type)
```

```{r}
class(x$Min.Price)
```
```{r}
class(x$Price)
```

```{r}
class(x$Max.Price)
```


Checking out the names of all features of `Cars93` data set at once:

```{r}
sapply(x, class)
```

and so on...

